$\pi$SOD-M: A Methodology for Building Service-Oriented Applications in the Presence of Non-Functional Properties

### 2014-03-13 JournalToSubmit2013/modelingWithPISODM.tex
Section transformation .. currently being modified

Model transformations can be seen as processes that take models as input and produces models as output. The $\pi$-SOD-M model transformations occur in the two levels, PIM and PSM, we defined: PIM-to-PIM and PIM-to-PSM transformations. Transformations in the same level are ?horizontal transformations?, and transformations between different levels are called ?vertical transformations?. There are 3 model transformations defined in $\pi$-SOD-M: $\pi$-UseCase to $\pi$--ServiceProcess; $\pi$--ServiceProcess to $\pi$-ServiceComposition; and $\pi$-ServiceComposition to $\pi$-PEWS.

@@

The PIM to PIM transformation process between $\pi$-UseCase and $\pi$-ServiceProcess (Table \ref{fig:transformationsUseCase-ServiceProcess}) models defines how the application requirements are represented as a service process. At this level, services and general functions are represented as simple or composite use cases.
\begin{figure}
\centering{
\includegraphics[width=0.96\textwidth]{figs/Table5}}
\caption{ $\pi$-UseCase to $\pi$-ServiceProcess transformation}
\label{fig:transformationsUseCase-ServiceProcess}
\end{figure}

Every {\sc Use Case} is transformed into an {\sc Action} of the $\pi$-ServiceProcess meta-model, and every {\sc Extend} association identified in the $\pi$-UseCase meta-model is transformed into a  {\sc Fork node}.
%because several extends relations implies a conditional verification in the execution workflow . 
If the extend association has only one {\sc Use Case}, the fork will present the {\sc Action} as an alternative flow, and later, both flows will meet. If the extend association has several source {\sc Use Case}, the fork will present different {\sc Actions} as mutual alternatives flows, and later, all these flows will meet.  {\sc Activity services} (from $\pi$-ServiceProcess meta-model) consists of a composition of one or more {\sc Actions}. {\sc Action} can be viewed as a method of the system application. Thus, services are represented as a set of functions in the $\pi$-ServiceProcess meta- model, because {\sc Contracts} modelled are associated to functions ({\sc Actions}).

@@

All {\sc Constraints} in the source model ($\pi$-UseCase meta-model) are transformed into a {\sc Contract}. A {\sc Contract} is represented as a set of {\sc Constraints}. Each constrain description is directly transformed into {\sc Assertion}. A set of {\sc Constraint} of a {\sc Use Case} or a {\sc Composite use case} is transformed into a set of {\sc Assertion} used to define a {\sc Contract}. All {\sc Use Cases} are associated to a {\sc Non-functional requirement} and all {\sc Constraints} are associated with a {\sc Non-functional attribute}. Thus, {\sc Constraint} representing the same {\sc Use Case} is transformed into a {\sc Contract}. A {\sc Contract} can have exceptional cases. The negation of the {\sc Constraint} predicate are treated as {\sc Exceptional behaviour}. In this particular case, a {\sc Exceptional behaviour} will be generated in the target model.
The {\sc Constraint type} can have different transformations, depending of the following values:
\begin{itemize}
\item If the value of {\sc Constraint type} is {\sc Business}, it will be transformed into none {\sc Assertion};
\item  If the value of {\sc Constraint type} is {\sc Value} with the {\sc Assertion} isExceptionalBehaviour attribute set to false, it will be transformed into one {\sc Assertion};
\item If the value of {\sc Constraint type} is {\sc Value} with the {\sc Assertion} isExceptionalBehaviour attribute set to true, it will be transformed into a {\sc Exceptional behaviour};
\end{itemize}
Given the $\pi$-UseCase meta-model, to all {\sc Constraint} entity related with a {\sc Use Case}, there is a {\sc Contract} that compounds a set of {\sc Assertions} entity (figure  \ref{fig:transformationsUseCase-ServiceProcessRules}-a) and the {\sc Use Case} is refined in a service {\sc Action}.

\begin{example}[To Publish Music \textit{(cont)}]\label{ex:toPublicMusicT1}
Considering the scenario example  the transformation of the ?listen music? Use Case is transformed into a Service Action. This Action is a Spotify service function that can be invoked to play the music. For ?publish music? Use Case, all Constraints are transformed in a set of Assertions that are grouped in a Contract (?publishMusicContract?). The ?publishMusicContract? is related with the ?publishMusic? Action. 
\end{example}

A {\sc Constraint} transformation means that from {\sc Constraint} and {\sc Constraint Type} entities are generated detailed {\sc Contract} information, that are refined into {\sc Exceptional behaviours} and {\sc Assertions} entities (figure   \ref{fig:transformationsUseCase-ServiceProcessRules}-b). {\sc Constraint} is related with a {\sc Constraint type}, and there are different cases for the transformation of this concept. A Business type is transformed into an {\sc Assertion} that does not consider value attributes information like maxValue and minValue. These {\sc  Assertion} information attributes are considered if the {\sc Constraint Type} is a Value type. This is semi-automatic, because there is not
enough information in a $\pi$-UseCase model to run a complete automatic transformation.

If the {\sc Constraint Type} is a Value type, the designer must specify the variable information, and its boundary values after the transformation. For this, the designer must consider the {\sc Constraint} and {\sc Use Case} descriptions. By default, value constraints are transformed into pre-conditions and business constraints are transformed into post-conditions. This rule may be adjusted by the designer at the time of transformation.

A {\sc Service activity} and the {\sc Actions} are generated from two different elements in the source model ($\pi$-UseCase), from a {\sc Requirement} or a {\sc Composite use case}. Figures  \ref{fig:transformationsUseCase-ServiceProcessRules}-c  and d present the transformation schema for {\sc Requirement} and {\sc Composite use case} concepts. Both elements are related with many {\sc Use Cases} that are transformed in many {\sc Actions}. A {\sc Use Case} is related with, either, a {\sc Requirement} and a {\sc Composite use case}. {\sc Actions} are related with a {\sc Service activity.}

\begin{example}[To Publish Music \textit{(cont)}]\label{ex:toPublicMusicT2}
For the execution of the ?download music? use case is necessary process with the payment process. Thus, the set of {\sc Use cases} that include the ?download music? process are transformed in {\sc Actions}, and a {\sc Service activity} that aggregates these {\sc Actions} is also generated. 
\end{example}

@@

\begin{example}[To Publish Music \textit{(cont)}]\label{ex:toPublicMusicT3}
Considering the scenario example, it is possible to apply the same rule for the ?publish music? use case, which has two extended use cases, ?public twitter? and ?public Facebook?, applying the illustration expressed in figures \ref{fig:transformaton-examples}-b and d.
\end{example}

@@

\begin{example}[To Publish Music \textit{(cont)}]\label{ex:toPublicMusicT4}
Example: Given the ?download music? use case from the scenario example, it includes pay- ment process to buy the music. It is represented as a include in the $\pi$-UseCase model and is transformed in a sequence flow in the $\pi$-ServiceProcess model (as presented in figure \ref{fig:transformation-example-include}). 
\end{example}

@@

All this transformation rules from $\pi$-UseCase model to $\pi$-ServiceProcess model were validated with the scenario example. All transformations described in this section are completely automatic, however information about values and its boundaries are inserted by the designer after the transformation process.

%In the scenario "To Publish Music" the service activity {\sf PublishMusic} of the $\pi$-SC model specifies  calls to two {\sf Activitie}s of type {\em UpdateMusic}, respectively concerning the {\sf Business Service}s {\em Facebook} and {\em Twitter}. Given that no {\sf ConstrolNode} is specified by the $\pi$-SC model, the corresponding transformation is the expression that defines a {\sf Composite Operation} named {\em PublishSong} of the $\pi$-{\sc Pews} model of the form ({\sf PublishFacebook} $\parallel$ {\sf PublishTwitter}).

% _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ .
%\noindent

%{\bf\em 
\subsubsection{From $\pi$-ServiceProcess to $\pi$-ServiceComposition}
% _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ .
%The {\em A-policies} defined for the elements of the $\pi$-SCM are transformed into {\sc A-Policy} classes, named according to the names expressed in the source model. The transformation of the rules expressed in the $\pi$-SCM is guided by the event types associated to these rules.   The variables associated to an {\em A-policy} expressed in the $\pi$-SCM as {\sc\em $<$Variable:name, Variable:type$>$} are transformed into elements of type {\sc Variable} with attributes {\sc name} and {\sc type} directly specified from the elements {\sc\em  Variable:name} and {\sc\em Variable:type} of the $\pi$-SCM model.

@@

%Figure \ref{fig:pewsexpression} shows the correspondence between the model and the statements that implement it, with a schematic representation of the business process.
%\begin{figure}
%\centering{
%\includegraphics[width=0.85\textwidth]{figs/pews-expression}}
%\caption{Pews program implementing the "To Publish Music" application}
%\label{fig:pewsexpression}
%\end{figure}

The main goal of this transformation is to group all {\sc Contracts} and {\sc Actions} in {\sc Policies} and {\sc Service activities}, respectively.
{\sc Actions}  in the source model will be transformed into an {\sc Action} in the target model, and every {\sc Service activity} in the source model will be transformed into a {\sc Service activity} in the target model. This happens because $\pi$-ServiceComposition is an extension of $\pi$-ServiceProcess.
For the non-functional specifications, the {\sc Contract} entity with the same {\sc Non-functional requirement} in the source model ($\pi$-ServiceProcess model) will be transformed into a {\sc Policy} in the target model ($\pi$-ServiceComposition model). Each {\sc Assertion} will be transformed into a {\sc Rule:Condition} attribute in the target model, but if the {\sc Assertion} has a value type, the name and the attributes in the source model will be transformed into a {\sc Variable} in the target model. The other {\sc Assertion property} values remains unchanged. The {\sc Assertion: Aproperty} attribute can have different transformations, depending of the following values:
\begin{itemize}
\item {\sc Post-Conditions} are transformed into{\sc  Post} in the $\pi$-ServiceComposition model; 
\item {\sc Preconditions} are transformed into {\sc Pre} in the $\pi$-ServiceComposition model;
\item {\sc Timerestrictions} are transformed into {\sc Time} in the $\pi$-ServiceComposition model.
\end{itemize}

@@

The {\sc Exceptional behaviour} entities will be transformed into an {\sc Action} in the $\pi$- ServiceComposition model, and every {\sc Non-functional attribute} associated to an element ({\sc Contract} and {\sc Non-functional requirement}) in the $\pi$-ServiceProcess model becomes a {\sc Non-functional attribute} associated to the corresponding element ({\sc Policy}) in the $\pi$-ServiceComposition model.
Table \ref{fig:ServiceProcess-ServiceComposition}  describes the transformations between $\pi$-ServiceProcess and $\pi$-ServiceComposition meta-models.

Figure \ref{fig:ServiceProcess-ServiceComposition-Rules} presents the main transformation rules for this level. The main feature of this transformation is the generation of a {\sc Policy} from of a set of {\sc Contracts}. But, what is the adopted criterion for this transformation? The main criteria is that all {\sc Contracts} from the same {\sc Non-functional requirement} will be transformed in one {\sc Policy}. Thus, we can have Safety, Performance, and Reliability {\sc Policies}.

Each {\sc Assertion} of a {\sc Contract} ( $\pi$-UseCase model) is transformed into a {\sc Rule} in the $\pi$-ServiceProcess model. The set of {\sc Contracts} generates a {\sc Policy} composed by those {\sc Rules}. Thus, the set of {\sc Rules} make up a single {\sc Policy}. It is important to highlight that only the {\sc Contracts} of the same {\sc Non-functional requirement} is transformed into the same {\sc Policy}. Different NFRs? {\sc Contracts}, are transformed into different {\sc Policies}. Figure \ref{fig:ServiceProcess-ServiceComposition-Rules}-a show how this transformation is made.
Similar to the transformation between {\sc Contract} and {\sc Policy}, a set of {\sc Actions} is transformed into a single {\sc Service activity} entity. {\sc Actions} are related with {\sc Business collaborator}, and all information related to a {\sc Business Collaborator} are transformed from {\sc Packages} information ($\pi$-UseCase model).  {\sc Packages} are transformed into {\sc Business Collaborator}. Figure \ref{fig:ServiceProcess-ServiceComposition-Rules}-b presents the transformation between {\sc Action} and {\sc Service Activity} elements.
An exceptional behaviour is triggered by a failure in the verification of the condition of a rule. An {\sc Exceptional behaviour} is performed to preserve the state of the application. Figure \ref{fig:ServiceProcess-ServiceComposition-Rules}-c presents how an {\sc Exceptional behaviour} that can be transformed into an {\sc Action} call.

As the $\pi$-ServiceComposition model refines the $\pi$-ServiceProcess concepts at PIM level, a service previously defined as actions (source model) is refined as composition of those actions (target model) that are necessary to represent a business service, identifying who are the partners involved in the realization ({\sc Business collaborators}). In addition, $\pi$-SOD-M defines a platform specific model based on web services composition. This model is explicitly indicates those actions which are (or will be, if not yet implemented) supported by web services.

\begin{example}[To Publish Music \textit{(cont)}]\label{ex:toPublicMusicT5}
Considering the scenario example, the {\sc Action}?s update music {\sc Contract} is transformed is a {\sc Policy} with its {\sc Rules}. All contract {\sc Assertions} are transformed in RULE and its attributes, e.g. the login and password verification. The ?securityLoginPolicy? is all set of {\sc Rules} that were transformed from the {\sc Assertions} in $\pi$-ServiceProcess model. The {\sc Non- functional requirement} information will be used to the {\sc Policy} generation comes from the initial use case model. Also the {\sc Business Collaborator} Facebook and Spotify information came from {\sc Package} $\pi$-UseCase entity element. All {\sc Contracts} of the same {\sc Non- functional requirement} are composed in a {\sc Policy}.
\end{example}
% _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ .
\subsection{From $\pi$-ServiceComposition to $\pi$-PEWS}
% _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ .

>>>>

 $\pi$-SOD-M  proposes  horizontal transformation rules between $\pi$-UseCase to $\pi$-ServiceProcess meta-models,  and vertical transformation rules between $\pi$--ServiceProcess to $\pi$-ServiceComposition meta models; and $\pi$-ServiceComposition to $\pi$-PEWS.

 %Transformations in the same level are ?horizontal transformations?, and transformations between different levels are called ?vertical transformations?. There are 3 model transformations defined in $\pi$-SOD-M: $\pi$-UseCase to $\pi$--ServiceProcess; $\pi$--ServiceProcess to $\pi$-ServiceComposition; and $\pi$-ServiceComposition to $\pi$-PEWS.

@@

The PIM to PIM transformation rules between $\pi$-UseCase and $\pi$-ServiceProcess meta-models (Table \ref{fig:transformationsUseCase-ServiceProcess})  specify how to express  simple and composite use cases defining the functions provided by the developed application, as a service process describing the application logic and its associated non-functional properties.  The principle is to express a set of $\pi$-use cases (i.e., use cases with constraints) related by associations of type {\sc Extend}   in terms of  actions related by a control flow and associated contracts.
\begin{figure}
\centering{
\includegraphics[width=0.96\textwidth]{figs/Table5}}
\caption{ $\pi$-UseCase to $\pi$-ServiceProcess transformation}
\label{fig:transformationsUseCase-ServiceProcess}
\end{figure}

Every {\sf Use Case} is transformed into an {\sf Action} defined in the $\pi$-ServiceProcess meta-model, and every {\sf Extend} association identified in a $\pi$-use case model is transformed into a  {\sf Fork node}.
If the extend association has only one {\sf use case},  the {\sf action} of the fork is an alternative flow. If the {\sf Extend} association has several source {\sf use cases},  different {\sf Actions} will mutual alternative flows of the fork node.  As shown in the $\pi$-ServiceProcess  meta-model an {\sc Activity service}  consists of a composition of one or more entities of type {\sc Action}.  {\sc Contracts}  are associated to  {\sc Actions}.

@@

   A {\sf Constraint} of a (composite) {\sf Use Case}  is transformed into an  {\sf Assertion}.  The set of constraints  in a $\pi$-UseCase model  transformed into assertions are grouped in a {\sf Contract} in a $\pi$-ServiceProcess model (figure  \ref{fig:transformationsUseCase-ServiceProcessRules}-a).
A constraint of a given type ({\sf Constraint type}) can have different transformations as stated in the following rules (figure   \ref{fig:transformationsUseCase-ServiceProcessRules}-b):
\begin{itemize}
\item  {\sc Business Constraint type} is transformed into any {\sf Assertion} that does not consider value attributes information like maxValue and minValue;
\item   {\sc Value Constraint type} is with the  {\sf  isExceptionalBehaviour}  set to false, is transformed into one {\sf Assertion};
\item  {\sc Value Constraint type}  with the {\sf  isExceptionalBehaviour } attribute set to true, is transformed into  {\sf Exceptional behaviour};
\end{itemize}
%Given the $\pi$-UseCase meta-model, to all {\sc Constraint} entity related with a {\sc Use Case}, there is a {\sc Contract} that compounds a set of {\sc Assertions} entity  and the {\sc Use Case} is refined in a service {\sc Action}.

 For {\sf Value Constraint Type}s
  the designer must specify value thresholds associated to variables according to the  { constraint}s  and {use case}s. By default, value constraints are transformed into pre-conditions and business constraints are transformed into post-conditions. This rule may be adjusted.

\begin{example}[To Publish Music \textit{(cont)}]\label{ex:toPublicMusicT1}
Considering the scenario example  the transformation of the "listen music" Use Case is transformed into a Service Action. This Action is a Spotify service function that can be invoked to play the music. For the "publish music" Use Case,  constraints are transformed in a set of assertions that are grouped in a Contract ("publishMusicContract"). The "publishMusicContract" is related with the Action "publishMusic". 
\end{example}

% From {\sc Constraint} and {\sc Constraint Type} entities are generated detailed {\sc Contract} information, that are refined into {\sc Exceptional behaviours} and {\sc Assertions} entities . {\sc Constraint} is related with a {\sc Constraint type}, and there are different cases for the transformation of this concept. A Business type is transformed into an {\sc Assertion} . These {\sc  Assertion} information attributes are considered if the {\sc Constraint Type} is a Value type. This is semi-automatic, because there is not
%enough information in a $\pi$-UseCase model to run a complete automatic transformation.

A {\sf Requirement} and a {\sf Composite use case} in a  $\pi$-UseCase model are transformed respectively into a {\sf Service activity} and an {\sf Action} (see figures  \ref{fig:transformationsUseCase-ServiceProcessRules}-c  and d).

\begin{example}[To Publish Music \textit{(cont)}]\label{ex:toPublicMusicT2}
For the use case "download music" it is necessary process  the payment. Thus, the use cases that model the function "download music"  are transformed into {\sf actions}, and a {\sf Service activity} that aggregates these {\sf Actions}. 
\end{example}

@@

\begin{example}[To Publish Music \textit{(cont)}]\label{ex:toPublicMusicT3}
Considering the scenario example, it is possible to apply the same rule for the "publish music" use case, which has two extended use cases, "public twitter" and "public Facebook", applying the illustration expressed in figures \ref{fig:transformaton-examples}-b and d.
\end{example}

@@

\begin{example}[To Publish Music \textit{(cont)}]\label{ex:toPublicMusicT4}
Given the "download music" use case from the scenario example, it includes pay- ment process to buy the music. It is represented as a include in the $\pi$-UseCase model and is transformed in a sequence flow in the $\pi$-ServiceProcess model (as presented in figure \ref{fig:transformation-example-include}). 
\end{example}

@@

% _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ .
\subsubsection{From $\pi$-ServiceProcess to $\pi$-ServiceComposition}
% _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ .
%The {\em A-policies} defined for the elements of the $\pi$-SCM are transformed into {\sc A-Policy} classes, named according to the names expressed in the source model. The transformation of the rules expressed in the $\pi$-SCM is guided by the event types associated to these rules.   The variables associated to an {\em A-policy} expressed in the $\pi$-SCM as {\sc\em $<$Variable:name, Variable:type$>$} are transformed into elements of type {\sc Variable} with attributes {\sc name} and {\sc type} directly specified from the elements {\sc\em  Variable:name} and {\sc\em Variable:type} of the $\pi$-SCM model.

@@

%Figure \ref{fig:pewsexpression} shows the correspondence between the model and the statements that implement it, with a schematic representation of the business process.
%\begin{figure}
%\centering{
%\includegraphics[width=0.85\textwidth]{figs/pews-expression}}
%\caption{Pews program implementing the "To Publish Music" application}
%\label{fig:pewsexpression}
%\end{figure}
Table \ref{fig:ServiceProcess-ServiceComposition}  describes the transformations between $\pi$-ServiceProcess and $\pi$-ServiceComposition meta-models.
Figure \ref{fig:ServiceProcess-ServiceComposition-Rules} presents the main transformation rules for this level. The  goal of this transformation  is to group all {\sf Contracts} and {\sf Actions} into {\sf Policies} and {\sf Service activities}, respectively.   The  criterion is that all {\sc Contracts} from the same {\sc Non-functional requirement} will be transformed into one {\sc Policy} type (e.g., safety, performance, and reliability {\sc Policy} types).

{\sf Actions}  are transformed into an {\sf Action} in the target model, and every {\sc Service activity} is transformed into a {\sf Service activity} in the target model. 
For the non-functional specifications, a {\sf Contract} entity with the same { non-functional requirement} in the source model ($\pi$-ServiceProcess model) is transformed into a {\sf Policy} in the target model ($\pi$-ServiceComposition model). Each {\sf Assertion} is transformed into a {\sf Rule:Condition} attribute in the target model, but if the {\sf Assertion} has a value type, the name and the attributes in the source model will be transformed into a {\sc Variable} in the target model. The other {\sf Assertion property} values remains unchanged. The {\sf Assertion: Aproperty} attribute can have different transformations, depending of the following values:
\begin{itemize}
\item {\sf Post-Conditions} are transformed into{\sf  Post} in a $\pi$-ServiceComposition model; 
\item {\sf Preconditions} are transformed into {\sf Pre} in a $\pi$-ServiceComposition model;
\item {\sf Timerestrictions} are transformed into {\sf Time} in a $\pi$-ServiceComposition model.
\end{itemize}

@@

The {\sc Exceptional behaviour} entities are transformed into an {\sf Action} in a $\pi$- ServiceComposition model, and every {\sf Non-functional attribute} associated to an element ({\sf Contract} and {\sf Non-functional requirement}) in the $\pi$-ServiceProcess model becomes a {\sf Non-functional attribute} associated to the corresponding element ({\sf Policy}) in the $\pi$-ServiceComposition model.

Each {\sc Assertion} of a {\sc Contract} ( $\pi$-UseCase model) is transformed into a {\sc Rule} in the $\pi$-ServiceProcess model. The set of {\sc Contracts} generates a {\sc Policy} composed by those {\sc Rules}. Thus, the set of {\sc Rules} make up a single {\sc Policy}. It is important to highlight that only the {\sc Contracts} of the same {\sc Non-functional requirement} is transformed into the same {\sc Policy}. Different NFRs {\sc Contracts}, are transformed into different {\sc Policies}. Figure \ref{fig:ServiceProcess-ServiceComposition-Rules}-a show how this transformation is made.
Similar to the transformation between {\sc Contract} and {\sc Policy}, a set of {\sc Actions} is transformed into a single {\sc Service activity} entity. {\sc Actions} are related with {\sc Business collaborator}, and all information related to a {\sc Business Collaborator} are transformed from {\sc Packages} information ($\pi$-UseCase model).  {\sc Packages} are transformed into {\sc Business Collaborator}. Figure \ref{fig:ServiceProcess-ServiceComposition-Rules}-b presents the transformation between {\sc Action} and {\sc Service Activity} elements.
An exceptional behaviour is triggered by a failure in the verification of the condition of a rule. An {\sc Exceptional behaviour} is performed to preserve the state of the application. Figure \ref{fig:ServiceProcess-ServiceComposition-Rules}-c presents how an {\sc Exceptional behaviour} that can be transformed into an {\sc Action} call.

%As the $\pi$-ServiceComposition model refines the $\pi$-ServiceProcess concepts at PIM level, a service previously defined as actions (source model) is refined as composition of those actions (target model) that are necessary to represent a business service, identifying who are the partners involved in the realization ({\sc Business collaborators}). 
%In addition, $\pi$-SOD-M defines a platform specific model based on web services composition. This model is explicitly indicates those actions which are (or will be, if not yet implemented) supported by web services.

\begin{example}[To Publish Music \textit{(cont)}]\label{ex:toPublicMusicT5}
Considering the scenario example, the {\sc Action}?s update music {\sc Contract} is transformed is a {\sc Policy} with its {\sc Rules}. All contract {\sc Assertions} are transformed in RULE and its attributes, e.g. the login and password verification. The "securityLoginPolicy" is all set of {\sc Rules} that were transformed from the {\sc Assertions} in $\pi$-ServiceProcess model. The {\sc Non- functional requirement} information will be used to the {\sc Policy} generation comes from the initial use case model. Also the {\sc Business Collaborator} Facebook and Spotify information came from {\sc Package} $\pi$-UseCase entity element. All {\sc Contracts} of the same {\sc Non- functional requirement} are composed in a {\sc Policy}.
\end{example}

% _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ .
\subsection{From $\pi$-ServiceComposition to $\pi$-PEWS}
% _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ . _ .
